Imbalanced-learn: A Python Toolbox to Tackle the Curse of Imbalanced Datasets in Machine Learning

### 2016-12-31 16-365.tex

\begin{abstract}%
  \texttt{imbalanced-learn} is an open-source python toolbox aiming at providing a wide range of methods to cope with the problem of imbalanced dataset frequently encountered in machine learning and pattern recognition.
  The implemented state-of-the-art methods can be categorized into four groups: (i) under-sampling, (ii) over-sampling, (iii) combination of over- and under-sampling, and (iv) ensemble learning methods.
  The proposed toolbox depends only on \texttt{numpy}, \texttt{scipy}, and \texttt{scikit-learn} and is distributed under MIT license.
  Furthermore, it is fully compatible with \texttt{scikit-learn} and is part of the \texttt{scikit-learn-contrib} supported project.
  Documentation, unit tests as well as integration tests are provided to ease usage and contribution.
  The toolbox is publicly available on GitHub \\ \url{https://github.com/scikit-learn-contrib/imbalanced-learn}.
\end{abstract}

@@

The class imbalance problem has been encountered in multiple areas such as
telecommunication managements, bioinformatics, fraud detection, and medical diagnosis,
and has been considered one of the top ten problems in data mining and
pattern recognition~\citep{yang200610,rastgoo2016tackling}.
Imbalanced data substantially compromises the learning process, since most of the
standard machine learning algorithms expect balanced class distribution or an
equal misclassification cost~\citep{he2009learning}. For this reason, several
approaches have been specifically proposed to handle such datasets.
Some of these methods have been implemented mainly in R language~\citep{torgo2010data,kuhn2015caret,dal2013racing}.
Up to our knowledge, there is no python toolbox allowing such processing while cutting edge machine learning toolboxes are available~\citep{pedregosa2011scikit,sonnenburg2010shogun}.

@@

The implementation relies on \texttt{numpy}, \texttt{scipy}, and \texttt{scikit-learn}.
Each sampler class implements three main methods inspired from the \texttt{scikit-learn} API:
(i) \texttt{fit} computes several statistics which are later needed to resample the data into a balanced set;
(ii) \texttt{sample} performs the sampling and returns the data with the desired balancing ratio;
and (iii) \texttt{fit\_sample} is equivalent to calling the method \texttt{fit} followed by the method \texttt{sample}.
A class \texttt{Pipeline} is inherited from the \texttt{scikit-learn}
toolbox to automatically combine \texttt{samplers},
\texttt{transformers}, and \texttt{estimators}.
Additionally, we provide some specific state-of-the-art metrics to evaluate
classification performance.

\bigbreak

>>>>

\begin{abstract}%
  \texttt{imbalanced-learn} is an open-source python toolbox aiming at providing a wide range of methods to cope with the problem of imbalanced dataset frequently encountered in machine learning and pattern recognition.
  The implemented state-of-the-art methods can be categorized into 4 groups: (i) under-sampling, (ii) over-sampling, (iii) combination of over- and under-sampling, and (iv) ensemble learning methods.
  The proposed toolbox depends only on \texttt{numpy}, \texttt{scipy}, and \texttt{scikit-learn} and is distributed under MIT license.
  Furthermore, it is fully compatible with \texttt{scikit-learn} and is part of the \texttt{scikit-learn-contrib} supported project.
  Documentation, unit tests as well as integration tests are provided to ease usage and contribution.
  Source code, binaries, and documentation can be downloaded from \url{https://github.com/scikit-learn-contrib/imbalanced-learn}.
\end{abstract}

@@

The class imbalance problem has been encountered in multiple areas such as
telecommunication managements, bioinformatics, fraud detection, and medical diagnosis,
and has been considered one of the top 10 problems in data mining and
pattern recognition~\citep{yang200610,rastgoo2016tackling}.
Imbalanced data substantially compromises the learning process, since most of the
standard machine learning algorithms expect balanced class distribution or an
equal misclassification cost~\citep{he2009learning}. For this reason, several
approaches have been specifically proposed to handle such datasets.
Some of these methods have been implemented mainly in R language~\citep{torgo2010data,kuhn2015caret,dal2013racing}.
Up to our knowledge, there is no python toolbox allowing such processing while cutting edge machine learning toolboxes are available~\citep{pedregosa2011scikit,sonnenburg2010shogun}.

@@

The implementation relies on \texttt{numpy}, \texttt{scipy}, and \texttt{scikit-learn}.
Each sampler class implements three main methods inspired from the \texttt{scikit-learn} API:
(i) \texttt{fit} computes several statistics which are later needed to resample the data into a balanced set;
(ii) \texttt{sample} performs the sampling and returns the data with the desired balancing ratio;
and (iii) \texttt{fit\_sample} is equivalent to calling the method \texttt{fit} followed by the method \texttt{sample}.
A class \texttt{Pipeline} is inherited from the \texttt{scikit-learn}
toolbox to automatically combine \texttt{samplers},
\texttt{transformers}, and \texttt{estimators}.
Additionally, we provide some specific state-of-the-art metrics to evaluate
classification performance.
\bigbreak
